Exploring the tree of numerical semigroups

### 2015-04-10 Papier/article.tex
Added thanks to L.G.

\textbf{Acknowledgment.} We would like to thank Shalom Eliahou for introducing us to the tree of numerical semigroups and for interesting
discussions on the subject. We also would like to thanks Nathan Cohen who
suggested the two levels of indirection stack optimization.

>>>>

\textbf{Acknowledgment.} We would like to thank Shalom Eliahou for introducing
us to the tree of numerical semigroups and for interesting discussions on the
subject. We are grateful to Laura Grigori who suggested us that Cilk could be
a good technology to tackle the tree-level parallelism for this kind of
problems.  We would finally like to thanks Nathan Cohen who suggested the two
levels of indirection stack optimization.
